combine all centers pheno

### 2020-12-17 scripts/40_combine_all_samp_pheno.Rmd
udpate

```{r}
# make proper columns factors as they should be

should_be_factors <- all %>% 
  select_if(is.character) %>% 
  select(-fid, -pt_id) %>% 
  colnames()

@@

```

```{r}
ALL %>% 
  split(.$center) %>% 
  map_dfr(~ count(x = ., icans), .id = 'center')
```
```{r}
ALL %>% 
  split(.$center) %>% 
  map_dfr(~ count(x = ., crs), .id = 'center')
```

@@

ALL %>% 
  select(outcome) %>% 
  map(function(col){
    ALL %>% 
  split(.$center) %>% 
  map_dfr(~ count(x = ., col), .id = 'center')
  })

for (i in 1:length(outcome)){
  ALL %>% 
    split(.$center) %>% 
    map_dfr(~ count(x = ., outcome[1]), .id = 'center')
}
```

>>>>

```{r}
# make proper columns factors as they should be 
should_be_factors <- all %>% 
  select_if(is.character) %>% 
  select(-fid, -pt_id) %>% 
  colnames()

@@

ALL %>% summary
```

@@

ALL %>% 
  count(center, cr_d100)

ALL %>% 
  count(center, toxicity)

ALL %>% 
  count(center, icans)

ALL %>% 
  count(center, crs)

tb <- ALL %>% 
  select(center, outcome) 
```
